
\documentclass[]{roshan-resume}
\usepackage{fancyhdr}
\usepackage{fontawesome5}

\pagestyle{fancy}
\pagecolor{pagecolor}
\fancyhf{}

\begin{document}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	%     LAST UPDATED DATE
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	%     TITLE NAME
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\namesection{}{Roshan Ali Shaik}{  Cyber Security Enthusiast | Bug Bounty Hunter \\
		\href{mailto:roshanalishaik003@gmail.com}{\faEnvelope\ roshanalishaik003@gmail.com} | 
		{\faPhone* \ +91 9014785786}
	}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	%     COLUMN ONE
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\begin{minipage}[t]{0.33\textwidth} 
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     LINKS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Social Links} 
		\faGithub \ \href{https://github.com/RoshanAli339}{github.com/RoshanAli339} \\
		\faLinkedinIn \  \href{https://www.linkedin.com/in/roshanali339/}{linkedin.com/in/roshanali339} \\
		\faYoutube \ \href{https://www.youtube.com/@cyberknight339}{@cyberknight339} \\
		\faMediumM \ \href{https://cyberknight339.medium.com}{CyberKnight339}
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     EDUCATION
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Education} 
		
		\subsection{\href{https://rvrjcce.ac.in/}{R.V.R \& J.C College of Engg.}}
		\descript{B.Tech in Computer Science and Engg.}
		\location{Currently pursuing | Guntur, India}
		\location{ Cum. GPA : 9.3 / 10.0}
		\sectionsep
		
		\subsection{JUPITER JUNIOR COLLEGE}
		\descript{Class XII}
		\location{May 2021 | Guntur, India}
		\location{96.7\%}
		\sectionsep
		
		\subsection{LOYOLA PUBLIC SCHOOL}
		\descript{Class X}
		\location{April 2019 | Guntur, India}
		\location{85\%}
		
		
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     SKILLS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Skills}
		\subsection{Cyber Security}
		\begin{itemize}
			\item Manual Web VAPT \\ 
			\item Network VAPT \\
			\item Compliance \\
			\item Reporting \& Documentation	
		\end{itemize}
		\subsection{Programming}
		\textbullet\ Java\ \textbullet\ C programming\ \textbullet\ C++\ \textbullet\ Python \\
		\textbullet\ HTML5\ \textbullet\ CSS3\ \textbullet\ JS\ \textbullet\ PHP 
		\sectionsep
		\subsection{Soft Skills}
		\textbullet\ Leadership\ \textbullet\ Communication\\
		\textbullet\ Organizational skills\ \textbullet Problem Solving \\
		\textbullet\ Decision Making 
		\sectionsep
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     TOOLS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\section{Tools}
		\subsection{Cyber Security}
		\begin{itemize}
			\item Kali Linux \\
			\item Parrot OS \\
			\item Wire Shark \\
			\item NMAP \\
			\item Metasploit \\
			\item BurpSuite
		\end{itemize}
		
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     CERTIFICATIONS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\section{Certifications}
		\begin{itemize}
			\item Google Cyber Security Professional
			\item Programming in Java, NPTEL
			\item Computer Networks \& Internet Protocol, NPTEL
			\item Programming, Data Structure \& Algorithms, NPTEL
			\item Problem Solving through Programming in C, NPTEL
		\end{itemize}
		
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%
		%     COLUMN TWO
		%
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
	\end{minipage} 
	\hfill
	\begin{minipage}[t]{0.66\textwidth} 
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     SUMMARY
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\section{About}
		Cyber Security enthusiast actively pursuing BTech in Computer Science with hands-on experience in bug bounty hunting. Proficient in vulnerability assessment, penetration testing, and network security. 
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     EXPERIENCE
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Experience}
		\runsubsection{\href{https://cybersapiens.com.au/}{CyberSapiens}}
		\descript{| Red Team Intern }
		\location{Jan 2023 - Jul 2023 | Guntur, India}
		\begin{itemize}
			\item Prepared extensive research on emerging web security threats and vulnerabilities to stay up-to-date with the latest trends. \\
			\item Conducted comprehensive penetration testing on web applications, successfully identifying and mitigating critical vulnerabilities including SQL injection, XSS, CSRF and more.
			\item Prepared comprehensive reports detailing
			vulnerabilities, their potential impact, and
			recommended mitigation measures. \\
			\item Engaged in ethical hacking activities to uncover
			security weaknesses and provide actionable insights for
			improvement.\\
			\item Conducted penetration tests to assess the resilience of
			web applications and networks against potential
			attacks.\\
		\end{itemize}
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     PROJECTS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\section{Projects}
		\subsection{Child Location Safety} 
		\begin{itemize}
			\item An IoT based child safety device to monitor his/her location.
			\item An android application built using Flutter to quickly check the child location.
			\item A full stack MERN (MySQL, Express JS, ReactJS, NodeJS) web application to store, manage and analyze the location details of the IoT device.
		\end{itemize}
		
		\subsection{NSE Web Scraper}
		\begin{itemize}
			\item Scraping live data from the National Stock Exchange India website
			\item Visualize live data in form of graphs and tables using polyplot and pandas
			\item Price prediction of stock prizes using Facebook prophet module.
		\end{itemize}
		
		\section{Leadership Experience}
		\runsubsection{ACM Student Chapter, R.V.R \& J.C College of Engineering} \hfill \location{Jan 2024 - Current}
		\begin{tightemize}
			\item Serving as the Chair, leading initiatives and have successfully organized \textbf{\textit{TECHNIZEN}}, a two-day intercollegiate event, attracting 1300 participants from 15 different institutions.
		\end{tightemize}
		\runsubsection{ISTE Student Chapter, R.V.R \& J.C College of Engineering}
		\hfill \location{Jan 2024 - Current}
		\begin{tightemize}
			\item Organized \textbf{MEDHANVESH}, an aptitutde test under the ISTE Student Chapter of our institute as one of the chief organizers, attracting 1500 participants.
		\end{tightemize}
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     ACHIEVEMENTS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Achievements} 
		\begin{itemize}
			\item Awarded \textbf{Intern of the Month} at \textit{CyberSapiens}, during my internship for the month of February 2023.
			\item Awarded \textbf{NPTEL Discipline Star} under Computer Science discipline.
			\item Secured 1\textsuperscript{st} place in \textit{Informatrix Coding Contest}, conducted at R.V.R \& J.C College of Engineering in November 2023.
			\item Achieved 1\textsuperscript{st} place in \textit{Digital Detective}, a debugging contest conducted at VVIT in August 2023.
			\item Ranked 2\textsuperscript{nd} place in \textit{CodeWiz Python Coding Contest} conducted at R.V.R \& J.C College of Engineering in July 2022.
		\end{itemize}
		
		

		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     ACTIVITES
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\section{Activities}
		\begin{itemize}
			\item Participated in \textbf{Udvikash} 24 hours Hackathon, organized by Institude Innovation Cell of R.V.R \& J.C COLLEGE OF ENGINEERING.
		\end{itemize}
		
	\end{minipage} 
\end{document}  \documentclass[]{article}