
\documentclass[]{roshan_resume}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	%     LAST UPDATED DATE
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	%     TITLE NAME
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\namesection{}{Roshan Ali Shaik}{  Cyber Security Enthusiast | Bug Bounty Hunter \\
		\href{mailto:roshanalishaik003@g.com}{roshanalishaik003@gmail.com} | {+91 9014785786}
	}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	%     COLUMN ONE
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\begin{minipage}[t]{0.33\textwidth} 
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     LINKS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Social Links} 
		Github:// \href{https://github.com/RoshanAli339}{\bf RoshanAli339} \\
		LinkedIn://  \href{https://www.linkedin.com/in/roshan-ali-shaik-011714222/}{\bf Roshan Ali} \\
		YouTube://  \href{https://www.youtube.com/@cyberknight339}{\bf CyberKnight339} \\
		
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     EDUCATION
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Education} 
		
		\subsection{\href{https://rvrjcce.ac.in/}{R.V.R \& J.C College of Engg.}}
		\descript{B.Tech in Computer Science and Engg.}
		\location{Currently pursuing| Guntur, India}
		\location{ Cum. GPA: 9.3 / 10.0}
		\sectionsep
		
		\subsection{JUPITETR JUNIOR COLLEGE}
		\descript{Class XII}
		\location{May 2021 | Guntur, India}
		\location{96.7\%}
		\sectionsep
		
		\subsection{LOYOLA PUBLIC SCHOOL}
		\descript{Class X}
		\location{April 2019 | Guntur, India}
		\location{85\%}
		
		
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     SKILLS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Skills}
		\subsection{Cyber Security}
		\textbullet{} Manual Web VAPT \\ 
		\textbullet{} Network VAPT \\
		\textbullet{} Compliance \\
		\textbullet{} Reporting \& Documentation
		\newline
		\subsection{Programming}
		\textbullet{} Python\\
		\textbullet{} Shell\\ 
		\textbullet{} Java \\
		\textbullet{} C  \\ 
		\textbullet{} CSS, Javascript \\
		\textbullet{} PHP, MySQL\\
		\sectionsep
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     TOOLS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\section{Tools}
		\subsection{Cyber Security}
		\textbullet{} Kali Linux \\
		\textbullet{} Parrot OS \\
		\textbullet{} Wire Shark \\
		\textbullet{} NMAP \\
		\textbullet{} Metasploit \\
		\textbullet{} BurpSuite
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%
		%     COLUMN TWO
		%
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
	\end{minipage} 
	\hfill
	\begin{minipage}[t]{0.66\textwidth} 
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     SUMMARY
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\section{About}
		Cyber Security enthusiast actively pursuing BTech in Computer Science with hands-on experience in bug bounty hunting. Proficient in vulnerability assessment, penetration testing, and network security. Eager to contribute technical skills to enhance digital security.
		\newline
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     EXPERIENCE
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Experience}
		\runsubsection{\href{https://cybersapiens.com.au/}{CyberSapiens}}
		\descript{| Red Team Intern }
		\location{Jan 2023 - Jul 2023 | Guntur, India}
		\begin{itemize}
			\item Conducted extensive research on emerging web security threats and vulnerabilities to stay up-to-date with the latest trends. \\
			\item Performed hands-on testing on web applications to identify vulnerabilities, including SQL injection, XSS,CSRF, and more.
			\item Prepared comprehensive reports detailing
			vulnerabilities, their potential impact, and
			recommended mitigation measures. \\
			\item Proficient in using various security tools and
			technologies such as Burp Suite, OWASP ZAP, and Nmap.\\
			\item Engaged in ethical hacking activities to uncover
			security weaknesses and provide actionable insights for
			improvement.\\
			\item Conducted penetration tests to assess the resilience of
			web applications and networks against potential
			attacks.\\
		\end{itemize}
		
		\sectionsep
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     CERTIFICATIONS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\section{Certifications}
		\subsection{Professional}
		\begin{itemize}
			\item Google Cyber Security Professional Certification
		\end{itemize}
		
		\subsection{Academic}
		\begin{itemize}
			\item Problem Solving Through Programming in C, NPTEL\\
			\item The Joy of Computing using Python, NPTEL\\
			\item Programming in Java, NPTEL\\
			\item Programming, Data Structures \& Algorithms, NPTEL\\
			\item Computer Networks and Internet Protocol, NPTEL
		\end{itemize}
		
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     ACHIEVEMENTS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\section{Achievements} 
		\begin{tabular}{rll}
			Feb 2023	     & \textbf{Intern of the Month}  & CyberSapiens\\
			May 2023         & NPTEL Discipline Star(CS) & NPTEL \\
			Nov 2023 		& 1\textsuperscript{st}/50 & Informatrix Coding Contest, RVRJC \\
			Aug 2023	     & 1\textsuperscript{st}/200  & Digital Detective, VVIT\\
			Aug 2023	     & 6\textsuperscript{th}/50  & Quanta Coding Contest, VRSEC\\
			Jul 2022     & 2\textsuperscript{nd}/100 & CodeWiz Coding Contest, RVRJC  \\
		\end{tabular}
		\sectionsep
		

		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     ACTIVITES
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\section{Activities}
		\begin{itemize}
			\item Attended the 2-day workshop on Ethical Hacking by \href{https://www.linkedin.com/company/remarkskill-education/about/}{Remarkskill} and \href{https://www.linkedin.com/company/ecell-iith/}{E-cell IIT Hyderabad}.\\
			\item Presented a working model on Web Scraper of NSE India using Python on Engineers Day 2023, at R.V.R \& JC COLLEGE OF ENGG. \\
			\item Participated in \textbf{Udvikash} 24 hours Hackathon, organized by Institude Innovation Cell of R.V.R \& J.C COLLEGE OF ENGINEERING.
		\end{itemize}
		
	\end{minipage} 
\end{document}  \documentclass[]{article}